Music Perception: Stimuli profiles

### 2021-06-07 material/expstimuli/stimuli.Rmd
correct comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>
calculate total number of performances
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

ioi <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Tempo)]
mean_ioi <- mean(ioi$Mean)
sd_ioi <- sd(ioi$Mean)
ioi_include <- ioi[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]

@@

## Histogram
- Exclude performances outside 2sd
- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)

1. Before exclusion
```{r plot-hist, echo = FALSE}
ioi$Tempo <- factor(ioi$Tempo)
gghistogram(ioi, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
gghistogram(ioi, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
```

2. After exclusion
```{r plot-hist2, echo = FALSE}
ioi_include$Tempo <- factor(ioi_include$Tempo)
gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
gghistogram(ioi_include, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
```

>>>>

ioi_original <- dt_ioi[Interval != 25 & Interval != 26 & Interval != 27 & Interval != 28 & Interval != 32 & Interval != 33 & Interval != 34 & Interval != 35 & Interval != 51 & Interval != 52 & Interval != 56 & Interval != 57 & Interval != 65 & Interval != 66 & Interval != 67 & Interval != 68 & Interval != 69 & Interval != 70 & Interval != 71, .(N = .N, Mean = mean(IOI), SD = sd(IOI)), by = .(SubNr, BlockNr, TrialNr, Tempo, Condition)]
mean_ioi <- mean(ioi_original$Mean)
sd_ioi <- sd(ioi_original$Mean)
ioi_include <- ioi_original[Mean < mean_ioi+2*sd_ioi & Mean > mean_ioi-2*sd_ioi]

@@

## IOIs Histogram
- Exclude performances outside 2sd
- Gray vertical lines indicate ideal tempi (300ms for 100bpm, 273ms for 110bpm, 250ms for 120bpm)

1. Before exclusion
```{r plot-hist, echo = FALSE}
ioi_original$Tempo <- factor(ioi_original$Tempo)
gghistogram(ioi_original, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
gghistogram(ioi_original, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
```
- the number of performances in the teaching condition: `r nrow(ioi_original[Condition == "teaching"])`
- the number of performances in the performing condition: `r nrow(ioi_original[Condition == "performing"])`

2. After exclusion
```{r plot-hist2, echo = FALSE}
ioi_include$Tempo <- factor(ioi_include$Tempo)
gghistogram(ioi_include, x = "Mean", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
gghistogram(ioi_include, x = "Mean", fill = "Tempo", color = "Tempo", rug = TRUE, add_density = TRUE, bins = 50) + geom_vline(xintercept = 	c(250, 273, 300), color = "gray", size = 1) + lims(y = c(0, 60))
```
- the number of performances in the teaching condition: `r nrow(ioi_include[Condition == "teaching"])`
- the number of performances in the performing condition: `r nrow(ioi_include[Condition == "performing"])`
